% Use values that are applicable to you and your thesis.

\newif\ifenglish{}
\englishtrue{} % english language
% \englishfalse{} % slovak language

\newif\ifbachelor{}
\bachelortrue{} % bachelor's thesis
% \bachelorfalse{} % master's thesis

\newif\ifcompsci{}
\compscitrue{} % computer science
% \compscifalse{} % bioinformatics

\newif\ifconsultant{}
% \consultanttrue{} % I have a consultant
\consultantfalse{} % no consultant

\newif\iflogoFMFI{}
% \logoFMFItrue{} % display the FMFI logo on the cover and the title page
\logoFMFIfalse{} % no logo

% The year in which you plan to turn the thesis in.
\newcommand{\thesisyear}{2024}

% Tip - use the `\\` to split a long thesis name nicely.
\newcommand{\thesisname}{Optimization of Variational Quantum Eigensolvers}

% If you are writing a master's thesis, don't forget to add Bc. here.
\newcommand{\thesisauthor}{Michal~Švec}

\newcommand{\thesissupervisor}{doc.~RNDr.~Martin~Plesch,~PhD. }

\newcommand{\thesisacknowledgments}{
    I would like to thank my supervisor \thesissupervisor for providing me with the opportunity to work on this thesis and for all his advice and time. Undoubtedly, other thanks go to his doctoral students who helped me understand challenging topics and provided me with valuable feedback and tips. 
}

\newcommand{\thesisabstractsk}{
    Dnešné kvantové počítače sa potýkaju s problémami ako chyby, šum a dekoherencia. Z tohto dôvodu bol uvedený hybridný kvantový algoritmus nazývaný variačný kvantový eigensolver (VQE), ktorý sa snaží tieto problémy zmierniť odovzdaním časti práce klasickým počítačom. Naša práca používa tento algoritmus na nájdenie základného stavu molekuly vodíka. Porovnávali sme výkonnosť viacerých parametrizovaných kvantových obvodov a optimalizačných algoritmov v ideálnych podmienkach. Výsledky ukazujú, že niektoré optimalizačné algoritmy založené na gradientoch poskytujú veľmi dobré výsledky bez ohľadu na parametrizované kvantové obvody. Veríme však, že iné optimalizačné algoritmy môžu dosiahnuť lepšie výsledky vyladením ich hyperparametrov.
}

\newcommand{\thesisabstracten}{
    Quantum computers of today's world suffer from errors, noise and decoherence. For this reason, there has been introduced a hybrid quantum algorithm called variational quantum eigensolver (VQE) that tries to mitigate these problems by handing some work to classical computers. Our work uses this algorithm to find the ground state energy of a hydrogen molecule. We have created a benchmark that evaluates the performance of multiple parametrized quantum circuits and optimizers in ideal conditions. The results show that some gradient-based optimizers provide very good results regardless of the parametrized quantum circuits. However, we believe that we can improve the results of other optimizers by tuning their hyperparameters.
}

\newcommand{\thesiskeywordssk}{kvantové počítače, variačný kvantový eigensolver, ansatz, optimalizačné algoritmy \ques{should I include there ansatz as Slovak word? :) or should I replace that with a ''parametrizovany kvantovy obvod''}}


\newcommand{\thesiskeywordsen}{quantum computers, variational quantum eigensolver, ansatz, optimization algorithms}

\newcommand{\thesischapters}{
    \input chapters/00-introduction.tex
    \input chapters/10-preliminaries.tex
    \input chapters/20-ansatz.tex
    \input chapters/30-variational-quantum-eigensolver.tex
    \input chapters/40-qiskit.tex
    \input chapters/50-experiments.tex
    \input chapters/60-conclusion.tex
}

\newcommand{\thesisappendices}{
    \input chapters/71-appendixA.tex
    % \input chapters/92-appendixB.tex
}

% Thesis type, field, programme, and department are set here automatically, but please check that
% the values are indeed correct for you.
% If your supervisor works at FMFI, set the \thesisdepartment to the supervisor's department (this
% one should also be present in the thesis assignment in AIS). Otherwise, keep the Department of
% Computer Science.
\ifenglish{}
    \ifbachelor{}
        \newcommand{\thesistype}{Bachelor's Thesis}
    \else
        \newcommand{\thesistype}{Master's Thesis}
    \fi
    \ifcompsci{}
        \newcommand{\thesisfield}{Computer Science}
        \newcommand{\thesisprogramme}{Computer Science}
    \else
        \newcommand{\thesisfield}{Computer Science and Biology}
        \newcommand{\thesisprogramme}{Bioinformatics}
    \fi
    \newcommand{\thesisdepartment}{Department of Computer Science}
    \newcommand{\thesisfaculty}{Faculty of Mathematics, Physics and Informatics}
    \newcommand{\thesisuniversity}{Comenius University in Bratislava}
\else
    \ifbachelor{}
        \newcommand{\thesistype}{Bakalárska práca}
    \else
        \newcommand{\thesistype}{Diplomová práca}
    \fi
    \ifcompsci{}
        \newcommand{\thesisfield}{Informatika}
        \newcommand{\thesisprogramme}{Informatika}
    \else
        \newcommand{\thesisfield}{Informatika a Biológia}
        \newcommand{\thesisprogramme}{Bioinformatika}
    \fi
    \newcommand{\thesisdepartment}{Katedra informatiky}
    \newcommand{\thesisfaculty}{Fakulta matematiky, fyziky a informatiky}
    \newcommand{\thesisuniversity}{Univerzita Komenského v Bratislave}
\fi
\newcommand{\thesislocation}{Bratislava}

% Helpers

\newif\ifshowframe{}
% \showframetrue{} % show page frames to debug positioning
\showframefalse{} % normal
